---
title: "P3_CrossSectional_EDA"
author: "Boyana Buyuklieva"
date: "August 30, 2022"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE, cache.lazy = FALSE)
library(data.table)
library(readr)

#library(dplyr)
#library(tidyverse)
#library(foreign)
#library(ggExtra)
#library(gridExtra)

source("../Outputs/Thesis_custom_scripts.R", local = knitr::knit_global())

combi_SC_dt <- loadRData( "../Data/RData_crossSectional/_combi_SC_dt_big_crossSect_EPCs_cleaned_N16m984358.RData")
```


TODO:


# NS Censorship

Exclusions:

X Built form unknown
X Age unknown
X 100 > EE & EEI > 0 [to fit into A - E], drops 'INVALID'. Then drop either nn_CEE_rating or CURRENT_ENERGY_RATING as these are the same. 
X Park homes, to small to count
X NUMBER_HABITABLE_ROOMS is NA or zero (loses 2M3 entries)
- remove 1% of floor area, which is 276 m2  (loses 168 792 entries)

Notes:
- Terrace (Mid;End;Enclosed Mid & Enclosed End)
- Flat (Flat & Maisonette)


```{r}
NS_dt <- combi_SC_dt

NS_dt <- NS_dt[ !nn_construction_age_band == 'unknown']
NS_dt <- NS_dt[ !nn_builtForm == 'unknown']

NS_dt <- NS_dt[ CURRENT_ENERGY_EFFICIENCY > 0 ]
NS_dt <- NS_dt[ CURRENT_ENERGY_EFFICIENCY < 101 ]

NS_dt <- NS_dt[ ENVIRONMENT_IMPACT_CURRENT > 0 ]
NS_dt <- NS_dt[ ENVIRONMENT_IMPACT_CURRENT < 101 ]
NS_dt[, nn_CEE_rating := NULL ]
#drop either nn_CEE_rating or CURRENT_ENERGY_RATING as these are the same after 0< values <101

NS_dt <- NS_dt[ !n_propTyp == 'Park home' ]
NS_dt <- NS_dt[ !is.na(NUMBER_HABITABLE_ROOMS) ]
NS_dt <- NS_dt[ !NUMBER_HABITABLE_ROOMS == 0 ]

maxthreshold <- round(quantile(NS_dt$TOTAL_FLOOR_AREA, 0.995, na.rm = T),0)
maxthreshold # 99.5% = 330m2, NOTE: 99.9% = 509m2
minthreshold <- round(quantile(NS_dt$TOTAL_FLOOR_AREA, 0.0001, na.rm = T),0) 
minthreshold # 0.01%  = 10m2

NS_dt <- NS_dt[ minthreshold < NS_dt$TOTAL_FLOOR_AREA,] 
NS_dt <- NS_dt[ maxthreshold > NS_dt$TOTAL_FLOOR_AREA,] # drops a further ~ 166 758

View( NS_dt[ TOTAL_FLOOR_AREA > 276 ,c('n_TOTAL_FLOOR_AREA', 'TOTAL_FLOOR_AREA'), with = F] )

#save(NS_dt, file ="../Data/RData_crossSectional/_NS_dt_N14m377170.RData")
```


























