---
title: "P3_CrossSectional_EDA"
author: "Boyana Buyuklieva"
date: "August 30, 2022"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE, cache.lazy = FALSE)
library(data.table)
library(readr)

#library(dplyr)
#library(tidyverse)
#library(foreign)
#library(ggExtra)
#library(gridExtra)

source("../Outputs/Thesis_custom_scripts.R", local = knitr::knit_global())
combi_SC_dt <- loadRData( "../Data/RData_crossSectional/_combi_SC_dt_big_crossSect_EPCs_cleaned_N16m984358.RData")
```


TODO:
# NS Censorship

Exclusions:

X Built form unknown
X Age unknown
X 100 > EE & EEI > 0 [to fit into A - E], drops 'INVALID'. Then drop either nn_CEE_rating or CURRENT_ENERGY_RATING as these are the same. 
X Park homes, to small to count
X NUMBER_HABITABLE_ROOMS is NA or zero (loses 2M3 entries)
X TENURE unknown
- remove 1% of floor area, which is 276 m2  (loses 168 792 entries)

Notes:
- Terrace (Mid;End;Enclosed Mid & Enclosed End)
- Flat (Flat & Maisonette)


```{r}
NS_dt <- combi_SC_dt

NS_dt <- NS_dt[ !nn_construction_age_band == 'unknown']# drops = 0
NS_dt <- NS_dt[ !nn_builtForm == 'unknown'] # drops = 2 305 479 

NS_dt <- NS_dt[ CURRENT_ENERGY_EFFICIENCY > 0 ] # drops = 0
NS_dt <- NS_dt[ CURRENT_ENERGY_EFFICIENCY < 101 ] # drops = 5

NS_dt <- NS_dt[ ENVIRONMENT_IMPACT_CURRENT > 0 ] # drops = 0
NS_dt <- NS_dt[ ENVIRONMENT_IMPACT_CURRENT < 101 ] # drops = 3 584 
NS_dt[, nn_CEE_rating := NULL ]
#drop either nn_CEE_rating or CURRENT_ENERGY_RATING as these are the same after 0< values <101

NS_dt <- NS_dt[ !n_propTyp == 'Park home' ] # drops = 0
NS_dt <- NS_dt[ !is.na(NUMBER_HABITABLE_ROOMS) ] # drops = 6 876 
NS_dt <- NS_dt[ !NUMBER_HABITABLE_ROOMS == 0 ] # drops = 215 545 

maxthreshold <- round(quantile(NS_dt$TOTAL_FLOOR_AREA, 0.997, na.rm = T),0)
maxthreshold # 99.7% / 379m2, NOTE: 99.9% = 509m2 / 99.5% = 330m2
minthreshold <- round(quantile(NS_dt$TOTAL_FLOOR_AREA, 0.0001, na.rm = T),0) 
minthreshold # 0.01%  = 10m2

NS_dt <- NS_dt[ minthreshold < NS_dt$TOTAL_FLOOR_AREA,] # drops = 2 535
NS_dt <- NS_dt[ maxthreshold > NS_dt$TOTAL_FLOOR_AREA,] # drops = 43 541

View( NS_dt[ TOTAL_FLOOR_AREA > 276 ,c('n_TOTAL_FLOOR_AREA', 'TOTAL_FLOOR_AREA'), with = F] )

#save(NS_dt, file ="../Data/RData_crossSectional/_NS_dt_N14m377170.RData")
NS_dt <- NS_dt[ !n_tenure == "unknown" ] # drops = 253 697
```




```{r geographies}
#avoid confusion
NS_dt[ ,LAD11NM:= NULL] 
NS_dt[ ,RGN11NM:= NULL] 

#Set the default region to be London
NS_dt[ ,RGN19NM:= relevel(as.factor(RGN19NM), 'London')]

#Set the default LAD to the worst perfoming one, Isles of Scilly
#View(NS_dt[ , .(mean = mean(CURRENT_ENERGY_EFFICIENCY)), by = LAD19NM])
#View(NS_dt[ , .(median = median(CURRENT_ENERGY_EFFICIENCY)), by = LAD19NM])
NS_dt[ ,LAD19NM:= relevel(as.factor(LAD19NM), 'Tower Hamlets')]
```

```{r}
date <- format(Sys.Date(), '_%Y%m%d')
#metaDataCSV( NS_dt , "NS_dt_N14m152777", dir = "../Data/_metaData/CSV_") #Adds date 
save(NS_dt, file ="../Data/RData_crossSectional/_NS_dt_N14m152777.RData")
```



















